Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-04-08 Manuscript_draft/Text.Rmd
edits

---
title: ''
output:
  pdf_document: default
  html_document: default
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
bibliography:
- references.bib
- knitcitations.bib
---
```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

>>>>

---
title: ''
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  word_document: default
  pdf_document: default
  html_document: default
bibliography:
- references.bib
- knitcitations.bib
---
```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```
